\Title

### 2013-01-24 synmut.tex
figures adapted

The central quantity we investigate is the probability of fixation of a
mutation, conditional on its population frequency.  A neutral mutation
segregating at frequency $\nu$ has a probability $P_\text{fix}(\nu) = \nu$ to
spread through the population and fix; in the rest of the cases, i.e. with
probability $1-\nu$, it goes extinct. As illustrated in the inset of \FIG{fixp},
this is a simple consequence of the fact that
(a) exactly one of the $N$ individuals in the current population will be
the common ancestor of the entire future population at a particular locus and
(b) this ancestor has a probability $\nu$ of carrying the mutation.
Deleterious or beneficial mutations fix less or
more often than neutral ones, respectively. Time series sequence data enable a
direct observation of both the current frequency $\nu$ of any particular
mutation and its future fate (fixation or extinction).

@@

\citet{bunnik_autologous_2008} present a longitudinal dataset on the entire
\env~gene of 3 patients at $\sim 5$ time points with approximately 5-20
sequences each (see methods). Repeating the above analysis separately on the
C2-V5 region studied above and the remainder of \env~ reveal striking
differences (see \FIG{fixp2}). Within C2-V5, this data fully confirms the
observations made in the data set by \citet{shankarappa_consistent_1999} (red
line). In the remainder of \env, however, observed synonymous mutations behave
neutrally (orange line).

>>>>

The central quantity we investigate is the probability of fixation of a
mutation, conditional on its population frequency.  A neutral mutation
segregating at frequency $\nu$ has a probability $P_\text{fix}(\nu) = \nu$ to
spread through the population and fix; in the rest of the cases, i.e. with
probability $1-\nu$, it goes extinct. As illustrated in the inset of \FIG{aftsyn},
this is a simple consequence of the fact that
(a) exactly one of the $N$ individuals in the current population will be
the common ancestor of the entire future population at a particular locus and
(b) this ancestor has a probability $\nu$ of carrying the mutation.
Deleterious or beneficial mutations fix less or
more often than neutral ones, respectively. Time series sequence data enable a
direct observation of both the current frequency $\nu$ of any particular
mutation and its future fate (fixation or extinction).

@@

\citet{bunnik_autologous_2008} present a longitudinal dataset on the entire
\env~gene of 3 patients at $\sim 5$ time points with approximately 5-20
sequences each (see methods). Repeating the above analysis separately on the
C2-V5 region studied above and the remainder of \env~ reveal striking
differences (see \FIG{fixp2}). Within C2-V5, this data fully confirms the
observations made in the data set by \citet{shankarappa_consistent_1999} (red
line). In the remainder of \env, however, observed synonymous mutations behave
neutrally (green line).
